\documentclass{article}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[pdfborder={0 0 0}]{hyperref}
\begin{document}
  
  \newcommand{\resumesection}[1]{\noindent \textbf{{\large #1}}}
  \newcommand{\breather}{\vspace{0.15in}}
  \newcommand{\ctilde}{\raise.17ex\hbox{$\sim$}}
  \newcommand{\techused}[1]{\small \textbf{Tech used:} #1}

  \pagestyle{empty}
  
  \noindent\textsf{\LARGE Christian Andrei B. Estioco}\\
  \textsf{\large BS Computer Science, University of the Philippines-Diliman\\
  Email: chadestioco@gmail.com $\cdot$ Portfolio: github.com/skytreader}
  \hline

  \vspace{0.1in}
  % BEST CRED: Numberphile and Computerphile regular viewer.
  \framebox[6in][c]{
    \parbox{6in}{\centering
      An online and up-to-date version of this document can be found at\\
      \url{https://github.com/skytreader/chad-cv}. This version was generated at 2022-05-09.
    }
  }
  \vspace{0.2in}
  \\
  \resumesection{Work Experience}
    \begin{itemize}
      \item \textbf{Senior Backend Gameplay Server Developer, GoodGame Studios (May 2019 - Present).}
      Fulfilled a hybrid DevOps role for games with over 53 million registered
      users worldwide. Developed features for both the actual gameplay and the
      revamped webshop system. Designed infrastructure solutions for features as
      well as various optimizations; in one project we reduced shop loading time
      by more than half.
      
      \techused{Java, Node, TypeScript, Vue.js, AWS (EC2, Lambda, API Gateway,
      S3, DynamoDB, etc.), Serverless, MySQL.}

      \item \textbf{DevOps/Site Reliability Engineer, Kalibrr (March 2017 - April 2019).}
      Improved mean response time of API endpoints some from \ctilde8000
      milliseconds to \ctilde900 milliseconds by reducing time spent in memory
      allocation. Reduced the build run time of backend unit tests by 42\% by
      reconfiguring tests to run in parallel. Helped in the migration of our 
      entire platform from Linode to GCP/GKE.
      
      \techused{Ansible, Angular 1, TypeScript, PostgreSQL, Redis, Elasticsearch,
      SASS, Bootstrap, Python, Pyramid, Celery, Docker, Kubernetes.}

      \item \textbf{Full Stack Web Developer, Kalibrr (February 2015 - March 2017).}
      Ensured usability of core features for mobile users, accounting for 62\% of Kalibrr's traffic
      at the time. Worked closely with Marketing and Design to strengthen acquisition
      through organic channels: acquired \ctilde100K users in three months with 95\% of
      acquisitions organic. Built features that helped ensure steady user growth despite seasonal lulls.

      \techused{Ansible, Angular 1, TypeScript, PostgreSQL, Redis, Elasticsearch,
      SASS, Bootstrap, Python, Pyramid, Celery.}
      
      \item \textbf{Research and Development Engineer, Chikka Philippines Inc. (September 2012 - November 2014).}
      Optimized the main infrastructure to ensure performance under heavy load.
      In one instance, I restructured a legacy component from \ctilde700k
      transactions over 9 hours to \ctilde1.5m transactions over 9 hours by
      refactoring database bottlenecks to use Redis. Also lead the development
      of an SMPP gateway, slated for use in more than two-thirds of Chikka's
      operations at the time.

      \techused{Java, Redis, MySQL, Python, Gevent, Java Servlets, ZeroMQ, SMPP,
      jQuery, Tornado, CentOS, RHEL, Ubuntu.}

      \item \textbf{Summer Intern, Azeus Systems Philippines Ltd. (April 2011 - May 2011).} Worked on a
      location-based social networking app for Android based on Google Maps with networking functionalities built
      on jWebSocket. Designed UI-mockups for the module assigned to my team. Implemented a
      messaging-like system as well as the map-based features of our module.

      \techused{Java, Android, Servlets, JSP, Google Maps, jWebSocket, Oracle.}
   \end{itemize}

  \resumesection{Research}
    \begin{itemize}
      \item \textbf{Undergraduate researcher, Computer Vision and Machine Intelligence Group (CVMIG), UP-Diliman
      (June 2011 - April 2012).} We created a system that recognizes Porites from images taken
      underwater using a search-based-on-texture approach, with a windowed Gabor Filter as an important component
      of the comparison. We managed an accuracy of 75-77\% on average but we achieved up to 80\% on a smaller
      window size. On top of this, I worked on possible alternate approaches, one of which lead us to our final
      algorithm.

      This is the first part of a multi-phase project for the Automated Rapid Reef Assessment System (ARRAS) which
      concluded in 2015.

      \techused{Java, JavaCV, Swing, Python, OpenCV, Octave.}
    \end{itemize}

  \resumesection{Hacks and Side-Projects}
    \begin{itemize}
      \item \textbf{Exkurzones.} (\url{https://github.com/skytreader/exkurzones})
      You have arrived at your assignment: a planet held captive by the evil Exkur Empire.
      Observing from a covert location at the atmosphere, you send your sabotage probe to
      destroy military outposts and free the planet. Unfortunately, the rebellion's
      intelligence and equipment is lacking. Can you destroy all the bases before
      The Empire's counterdefense detects your presence?

      This was created as an entry to the Good Game Jam 2020.
      
      \techused{JavaScript, Phaser 3}

      \item \textbf{PyGame Objects.} (\url{https://github.com/skytreader/PyGame-Objects})
      An experimental framework for building games with PyGame. The design philosophy behind the framework
      is to make it feel like writing a web MVC app.

      \techused{Python, PyGame.}

      \item \textbf{Alexandria.} (\url{https://github.com/skytreader/alexandria})
      A simple web app I built to catalog the books in my personal library. The goal is to
      get a relationship graph among the books I read where relationships are defined
      by the people who worked on the book.

      \techused{Python, Flask, MySQL, jQuery.}

      \item \textbf{Museician.} (\url{https://github.com/skytreader/museician})
      A music player for Android that plays songs after a specified delay, allowing
      users to ``prepare" to play along with the song. Google Play link:
      \url{https://goo.gl/KZySTx}.

      \techused{Java, Android.}
    \end{itemize}

  \breather
  \resumesection{Hobbies and Personal Interests\\}
  I volunteered for PythonPH, a Python User Group in the Philippines that holds PyConPH. I helped organize PyConPH 2014 and
  I was a speaker for PyconPH 2015 as well as during some monthly meet-ups. Slides of my talks can be found at \url{https://speakerdeck.com/skytreader}.

  Aside from coding, I enjoy reading artistic literature, making sketches, and practicing Taekwondo. I am also interested in
  calligraphy and amateur photography. Some of my amateur photographs can be found at \url{http://chadestioco.deviantart.com} .
  
\end{document}
